---
title: "Snapchat Politcal Ads Analysis"
author: "Lukas Lehmann"
date: "2024-09-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(janitor)
library(plotly)

snap_political_ads <- read_csv("data/PoliticalAds(4)/PoliticalAds.csv") %>%
  clean_names()

```

```{r}
us_ads <- snap_political_ads %>%
  filter(country_code == "united states")
  
us_ads_summary <- us_ads %>%
  group_by(paying_advertiser_name) %>%
  summarize(total_impressions = sum(impressions),
            total_spend = sum(spend)) %>%
  arrange(desc(total_spend))

top_10_spenders <- head(us_ads_summary$paying_advertiser_name, 10)

organization_1 <- top_10_spenders[1]
organization_2 <- top_10_spenders[2]
organization_3 <- top_10_spenders[3]
organization_4 <- top_10_spenders[4]
organization_5 <- top_10_spenders[5]
organization_6 <- top_10_spenders[6]
organization_7 <- top_10_spenders[7]
organization_8 <- top_10_spenders[8]
organization_9 <- top_10_spenders[9]
organization_10 <- top_10_spenders[10]

# Create a list of filtered tables for top 10 spenders
org_ads_list <- lapply(top_10_spenders, function(advertiser_name) {
  us_ads %>%
    mutate(impressions_per_dollar = impressions/spend) %>%
    filter(paying_advertiser_name == advertiser_name) %>%
    select(paying_advertiser_name, spend, impressions, 
           candidate_ballot_information, creative_url,
           start_date, end_date) %>%
    # Convert creative_url to clickable links
    mutate(creative_url = paste0("<a href='", creative_url, "' target='_blank'>Link</a>"))
})

# Name the list elements for easier reference
names(org_ads_list) <- top_10_spenders
  
```

# Ads from Top 10 Advertisers {.tabset}

The following is a collection of tables where you can see the actual text used in the titles and bodies of the advertisements. They are sorted in each tab by effectiveness - measured by impressions per dollar spent on advertisement.

It is possible to scroll left/right and click the page numbers at the bottom to see more information from that advertiser.

## `r top_10_spenders[1]`
```{r}
DT::datatable(org_ads_list[[1]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r top_10_spenders[2]`
```{r}
DT::datatable(org_ads_list[[2]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r top_10_spenders[3]`
```{r}
DT::datatable(org_ads_list[[3]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r top_10_spenders[4]`
```{r}
DT::datatable(org_ads_list[[4]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r top_10_spenders[5]`
```{r}
DT::datatable(org_ads_list[[5]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r top_10_spenders[6]`
```{r}
DT::datatable(org_ads_list[[6]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r top_10_spenders[7]`
```{r}
DT::datatable(org_ads_list[[7]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r top_10_spenders[8]`
```{r}
DT::datatable(org_ads_list[[8]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r top_10_spenders[9]`
```{r}
DT::datatable(org_ads_list[[9]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r top_10_spenders[10]`
```{r}
DT::datatable(org_ads_list[[10]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```


```{r harris data prep}

harris_ads <- us_ads %>%
  filter(str_detect(candidate_ballot_information, "Harris"))

harris_ads_summary <- harris_ads %>%
  group_by(paying_advertiser_name) %>%
  summarize(total_impressions = sum(impressions),
            total_spend = sum(spend)) %>%
  arrange(desc(total_spend))

# Extract top 7 advertisers based on total spending from harris_ads_summary
harris_advertisers <- head(harris_ads_summary$paying_advertiser_name, 7)

# Create individual variables for the top 7 organizations
organization_1 <- harris_advertisers[1]
organization_2 <- harris_advertisers[2]
organization_3 <- harris_advertisers[3]
organization_4 <- harris_advertisers[4]
organization_5 <- harris_advertisers[5]
organization_6 <- harris_advertisers[6]
organization_7 <- harris_advertisers[7]

# Create a list of filtered tables for the top 7 spenders
harris_ads_list <- lapply(harris_advertisers, function(advertiser_name) {
  us_ads %>%
    mutate(impressions_per_dollar = impressions/spend) %>%
    filter(paying_advertiser_name == advertiser_name) %>%
    select(paying_advertiser_name, spend, impressions, 
           candidate_ballot_information, creative_url,
           start_date, end_date) %>%
    # Convert creative_url to clickable links
    mutate(creative_url = paste0("<a href='", creative_url, "' target='_blank'>Link</a>"))
})

# Name the list elements for easier reference
names(harris_ads_list) <- harris_advertisers

  
```

# Harris - Official Campaign Spending

```{r}
harris_ads_official <- harris_ads %>%
  filter(paying_advertiser_name == "Harris for President") %>%
  mutate(start_date = as.Date(ymd_hms(start_date)),
         end_date = as.Date(ymd_hms(end_date)))

# Step 1: Create a sequence of dates for each ad
harris_ads_expanded <- harris_ads_official %>%
  # Generate a sequence of dates from start_date to end_date
  mutate(date_range = purrr::map2(start_date, end_date, seq, by = "day")) %>%
  # Expand rows so that each date in date_range has its own row
  unnest(date_range) %>%
  # Step 2: Calculate daily spend for each ad
  group_by(adid) %>%
  mutate(daily_spend = spend / n()) %>%
  ungroup()

# Step 3: Summarize daily spend across all ads
daily_spending <- harris_ads_expanded %>%
  group_by(date_range) %>%
  summarize(total_daily_spend = sum(daily_spend)) %>%
  arrange(date_range)

# Step 4: Visualize using ggplot2 and plotly
p <- ggplot(daily_spending, aes(x = date_range, y = total_daily_spend)) +
  geom_line(color = "blue", size = 1.2) +
  labs(title = "Harris for President - Daily Ad Spending",
       x = "Date",
       y = "Total Spending ($)") +
  theme_minimal()

# Convert ggplot to plotly
ggplotly(p)

aug_30_ads <- harris_ads %>%
  filter(as.Date(start_date) == as.Date("2024-09-10"))

# Display the filtered ads
aug_30_ads$creative_url

unique(harris_ads_official$regions_included)

```

# Pro-Harris Advertisers {.tabset}

## `r harris_advertisers[1]`
```{r}
DT::datatable(harris_ads_list[[1]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r harris_advertisers[2]`
```{r}
DT::datatable(harris_ads_list[[2]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r harris_advertisers[3]`
```{r}
DT::datatable(harris_ads_list[[3]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r harris_advertisers[4]`
```{r}
DT::datatable(harris_ads_list[[4]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r harris_advertisers[5]`
```{r}
DT::datatable(harris_ads_list[[5]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r harris_advertisers[6]`
```{r}
DT::datatable(harris_ads_list[[6]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r harris_advertisers[7]`
```{r}
DT::datatable(harris_ads_list[[7]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```


```{r trump data prep}

trump_ads <- us_ads %>%
  filter(str_detect(candidate_ballot_information, "Trump"))

trump_ads_summary <- trump_ads %>%
  group_by(paying_advertiser_name) %>%
  summarize(total_impressions = sum(impressions),
            total_spend = sum(spend)) %>%
  arrange(desc(total_spend))

# Extract top 7 advertisers based on total spending from trump_ads_summary
trump_advertisers <- head(trump_ads_summary$paying_advertiser_name, 7)

# Create individual variables for the top 7 organizations
organization_1 <- trump_advertisers[1]
organization_2 <- trump_advertisers[2]
organization_3 <- trump_advertisers[3]
organization_4 <- trump_advertisers[4]
organization_5 <- trump_advertisers[5]
organization_6 <- trump_advertisers[6]
organization_7 <- trump_advertisers[7]

# Create a list of filtered tables for the top 7 spenders
trump_ads_list <- lapply(trump_advertisers, function(advertiser_name) {
  us_ads %>%
    mutate(impressions_per_dollar = impressions/spend) %>%
    filter(paying_advertiser_name == advertiser_name) %>%
    select(paying_advertiser_name, spend, impressions, 
           candidate_ballot_information, creative_url,
           start_date, end_date) %>%
    # Convert creative_url to clickable links
    mutate(creative_url = paste0("<a href='", creative_url, "' target='_blank'>Link</a>"))
})

# Name the list elements for easier reference
names(trump_ads_list) <- trump_advertisers

  
```

# Pro-Trump Advertisers {.tabset}

## `r trump_advertisers[1]`
```{r}
DT::datatable(trump_ads_list[[1]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r trump_advertisers[2]`
```{r}
DT::datatable(trump_ads_list[[2]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r trump_advertisers[3]`
```{r}
DT::datatable(trump_ads_list[[3]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r trump_advertisers[4]`
```{r}
DT::datatable(trump_ads_list[[4]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r trump_advertisers[5]`
```{r}
DT::datatable(trump_ads_list[[5]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r trump_advertisers[6]`
```{r}
DT::datatable(trump_ads_list[[6]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```
## `r trump_advertisers[7]`
```{r}
DT::datatable(trump_ads_list[[7]], options = list(scrollX = TRUE, pageLength = 5), escape = FALSE)
```

